Fractional Types

### 2013-02-24 frac.tex
_

It is important to note that ``values'' and ``isomorphisms'' are completely
separate syntactic categories which do not intermix. The semantics of the
language come when these are made to interact at the ``top level'' via
\emph{application}:
%subcode{bnf} include main
% top level term, l ::= c v

@@

@@

% \roshan{It is unclear how fractions help differentiate between inputs
%   and outputs. On first reading this seemed promising, but nothing
%   in the rest of the paper substantiates this point of view.}
% AMR: a function a -o b is modeled by (1/a,b) not (a,b) 
% Jacques: Exactly!  1/a is negative information is input, b is positive is
%    output.
%

>>>>

It is important to note that ``values'' and ``isomorphisms'' are completely
separate syntactic categories which do not intermix. The semantics of the
language come when these are made to interact at the ``top level'' via
\emph{application}: \roshan{I understand its intent, but this last sentence is unclear.}
%subcode{bnf} include main
% top level term, l ::= c v

@@

\roshan{Suggestion : This para is a good one to delete if we run out
  of space. This is largely general knowledge about universal algebra
  and maybe one useful remark about the categorical structure. However
  we have a whole paper about the categorical structure of Pi at RC
  itself. My point is this sort of this can be a remark inserted at
  other places in passing and it doesn't deserve a para on its own. It
  teaches the reader nothing new about Pi. }

@@

% \roshan{It is unclear how fractions help differentiate between inputs
%   and outputs. On first reading this seemed promising, but nothing
%   in the rest of the paper substantiates this point of view.}
% AMR: a function a -o b is modeled by (1/a,b) not (a,b) 
% Jacques: Exactly!  1/a is negative information is input, b is positive is
%    output.
%
% Roshan: I completely understand this and this is not my objection. This
% is not what the above sentence is saying however. Its talking about
% Pi not having a notion of input and output which is simply
% confusing.
